Won’t you be my neighboR?

### 2019-05-15 msu-workshop-2019.Rmd
update post conversation with Emily

library(knitr)
```

@@

@@

@@

@@

```{r}
tibble(var1 = c("a", "b", "c"),
       var2 = c(4, 2, 5))
```

@@

@@

```{r}
vec <- runif(10) # generates random number between 0 and 1
ifelse(vec >= .5, "greater", "lesser")
```

@@

```{r}
d1 <- tibble(var1 <- runif(10))
d1 %>% 
  mutate(var2 = case_when(
    vec >= .5 ~ "greater",
    vec < .5 ~ "lesser"
  ))
```

@@

@@

@@

# Visualizing data

@@

@@

# Processing data

@@

**For more information on tidy data, check out [Hadley Wickhams's Tidy Data paper](http://vita.had.co.nz/papers/tidy-data.html).**
**For more information on the Tidyverse, check out DataCamp's [Getting Started with the Tidyverse tutorial]( https://www.datacamp.com/community/tutorials/tidyverse-tutorial-r).**

@@

**For more information on installing R and R Studio, check out DataCamp's [R Data Import Tutorial](https://www.datacamp.com/community/tutorials/installing-R-windows-mac-ubuntu).**

@@

# Creating reproducible reports

>>>>

library(knitr)
library(tidyverse)
```

@@

class: inverse, center, middle

@@

# Using packages

@@

# Objects and variables

```{r}
my_object <- 1
my_other_object <- c(1:10)
```

Reading in a CSV and assigning it to an object

```{r}
my_df <- read_csv("example-data.csv")
my_df
```

@@

```{r}
library(tidyverse)
tibble(var1 = c("a", "b", "c"),
       var2 = c(4, 2, 5))
```

@@

```{r}
vec1 = c("a", "b", "c")
vec1 
```

```{r}
vec2 = c(4, 2, 5)
vec2
```

```{r}
library(tibble)
tibble(var1 = vec1,
       var2 = vec2)
```

@@

```{r}
vec1 <- runif(10) # generates random number between 0 and 1
d1 <- tibble(var1 = vec1)

d1 %>% 
  mutate(var2 = ifelse(vec1 >= .5, "greater", "lesser"))
```

@@

```{r}
d1 %>% 
  mutate(var2 = case_when(
    var1 >= .75 ~ "a lot",
    var1 >= .5 ~ "greater",
    var1 < .5 ~ "lesser",
    var1 <= .25 ~ "very little" 
  ))
```

@@

```{r}
mean(c(1, 2, 3))
```

```{r}
mean(c(1, 2, 3, NA))
```

```{r, eval = FALSE}
?mean
```

```{r}
mean(c(1, 2, 3, NA), na.rm = TRUE)
```

```{r, eval = FALSE}
library(tidyverse)
read_directory <- function(directory) {
  map_df(list.files(directory), read_csv)
}

d <- read_directory("data")
```

@@

```{r}
random_numbers <- rnorm(n = 10, mean = 0)
random_numbers
mean(random_numbers)
sd(random_numbers)
```

```{r}
library(tidyverse)
1:10 %>%
  map(~ rnorm(n = 10, mean = .x)) %>%
  map_dbl(mean)
```

@@

class: inverse, center, middle
# Visualizing data

@@

---
class: inverse, center, middle
# Processing data

@@

@@

**For more information on tidy data, check out [Hadley Wickhams's Tidy Data paper](http://vita.had.co.nz/papers/tidy-data.html).**

@@

@@

class: inverse, center, middle
# Creating reproducible reports
